Privacy-Preserving Localization Using Private Linear-Combination Aggregation

### 2021-05-27 main.tex
Draft of leakage section completed

\begin{remark} \label{rem:lcao_leakage}

@@

Lastly, we make the following remark about a possible implicit weight.
\begin{remark} \label{rem:lcao_implicit_weight}
    The construction of the above scheme supports linearly combining the implicit weight $\omega^{(t)}_j = 1$, by replacing
    \begin{equation}
        \mathcal{E}_{pk_0}(1)^{a^{(t)}_{i,j}} = (N+1)^{1}\rho_j^N \pmod{N^2}
    \end{equation}
    in \eqref{eqn:our_scheme_lin_comb}, by
    \begin{equation}
        (N+1)^{a^{(t)}_{i,j}} \pmod{N^2}\,.
    \end{equation}
    This is due to the removal of $\rho_j^N$ terms during decryption and can be used to reduce the navigator's broadcast communication cost by a single weight when it is known that $\omega^{(t)}_j=1$.
\end{remark}

@@

    \State Let $\alpha_{v}^{(i)}$ represent an encryption of element $v$ in $\vec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
    \State $\alpha_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}y^2_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^2_{k|k-1}))^{\mathsf{E}_{0}(-r_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(y^2_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1}z_{k,i}')}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{-1}s_{x,i}^2)}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{-1}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(2r_{k,i}^{-1}s_{x,i}^3)}
    (N+1)^{\mathsf{E}_{1}(2r_{k,i}^{-1}s_{x,i}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(-2r_{k, i}^{-1}s_{x,i}z_{k,i}')}
    H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
    \State Compute $\alpha_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and remark \ref{rem:lcao_implicit_weight} in the form above
    \For{$v \gets 1$ to $2$}
        \State Send $\alpha_{v}^{(i)}$ to the navigator
    \EndFor

    \State Let $\beta_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^2_{k|k-1}))^{\mathsf{E}_{0}(4r_{k,i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-8r_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(4r_{k,i}^{-1}s_{x,i}^2)}\cdot$\par
    \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
    \State Compute remaining $\beta_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and remark \ref{rem:lcao_implicit_weight} in the form above
    \For{$v \gets 1$ to $2$}
        \For{$w \gets 1$ to $2$} 
            \State Send $\beta_{vw}^{(i)}$ to the navigator
        \EndFor
    \EndFor
    \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\subsection{Leakage} \label{subsec:leakage}
With the algorithm defined, we can analyze the localization leakage when the strictly defined LCAO leakage is taken into account. We recall the assumptions on participant capabilities made in Section . Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage. Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements when navigator behavior is dependent on its estimate. This may be achievable by detecting changes in measurements after reporting false ones. As misbehaving sensors are also a known problem which complicates homomorphic operations, active malicious sensors are not considered in the scope of this work.

The aggregation operation of our encryption scheme leaks the sums of sensor measurement vectors and matrices $\sum_{i=1}^n\rvec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, however, as stated in Remark \ref{rem:lcao_leakage}, weights chosen by a corrupted navigator mean that individual sums of coefficients can be leaked as well. That is, sums of coefficients in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} (\textit{i.e.}, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}$, $\sum_{i=1}^n-\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n-2\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}\rv{z}'_{k,i}$, \dots) are leaked to a corrupted navigator.

From the leaked sums of coefficients, we see that all information private to the sensors and broadcast to the navigator, namely their modified measurements $\rv{z}'_{k,i}$, variance estimates $\rv{r}_{k,i}$ and locations $\vec{s}_i$, are present only in the sums
\begin{equation}
    \sum_{i=1}^n\rv{z}'_{k,i}\,,\ \sum_{i=1}^n\rv{r}_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,.\label{eqn:localization_leakage}
\end{equation}
From these sums and the definitions \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate}, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor modified measurements, estimated variances and locations.
\begin{theorem}
    In the context of our localization scheme, leakage of the incorporated LCAO secure encryption scheme corresponds to the leakage of average sensor private information, given by the sums in \eqref{eqn:localization_leakage}.
\end{theorem}

>>>>

\begin{remark}

@@

Lastly, we make the following remark about a possible implicit weight.
\begin{remark}
    The construction of the above scheme supports linearly combining the implicit weight $\omega^{(t)}_j = 1$, by replacing
    \begin{equation}
        \mathcal{E}_{pk_0}(1)^{a^{(t)}_{i,j}} = (N+1)^{1}\rho_j^N \pmod{N^2}
    \end{equation}
    in \eqref{eqn:our_scheme_lin_comb}, by
    \begin{equation}
        (N+1)^{a^{(t)}_{i,j}} \pmod{N^2}\,.
    \end{equation}
    This is due to the removal of $\rho_j^N$ terms during decryption and can be used to reduce the navigator's broadcast communication cost by a single weight when it is known that $\omega^{(t)}_j=1$.
\end{remark}

@@

    \State Let $\alpha_{v}^{(i)}$ represent an encryption of element $v$ in $\vec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
    \State $\alpha_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}y^2_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^2_{k|k-1}))^{\mathsf{E}_{0}(-r_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(y^2_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1}z_{k,i}')}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{-1}s_{x,i}^2)}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{-1}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(2r_{k,i}^{-1}s_{x,i}^3)}
    (N+1)^{\mathsf{E}_{1}(2r_{k,i}^{-1}s_{x,i}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(-2r_{k, i}^{-1}s_{x,i}z_{k,i}')}
    H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
    \State Compute $\alpha_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
    \For{$v \gets 1$ to $2$}
        \State Send $\alpha_{v}^{(i)}$ to the navigator
    \EndFor

    \State Let $\beta_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^2_{k|k-1}))^{\mathsf{E}_{0}(4r_{k,i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-8r_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(4r_{k,i}^{-1}s_{x,i}^2)}\cdot$\par
    \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
    \State Compute remaining $\beta_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
    \For{$v \gets 1$ to $2$}
        \For{$w \gets 1$ to $2$} 
            \State Send $\beta_{vw}^{(i)}$ to the navigator
        \EndFor
    \EndFor
    \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\subsection{Leakage} \label{subsec:leakage}
With the privacy-preserving EIF defined in the previous section, we can now interpret the aggregation leakage of an LCAO scheme in the context of range sensor localisation. The leakage function from the $\mathsf{AggDec}$ algorithm corresponds to the information vector and matrix sums $\sum_{i=1}^n\vec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, respectively. However, recalling the remark in section \ref{subsec:crypto_problem}, a compromised navigator can also learn the individual sums weighted by the same weight, which in this case means the leakage of $\{\sum_{i=1}^n2r^{-1}_{k,i},\ \sum_{i=1}^n-r^{-1}_{k,i}s_{x,i},\ \sum_{i=1}^n-2r^{-1}_{k,i}s_{x,i},\ \dots\}$. From these leaked sums, we can see that private sensor information, $z'_{k,i}$, $r_{k,i}$ and $\vec{s}_i$, is present only in their complete sums
\begin{equation}
    \sum_{i=1}^nz'_{k,i}\,,\ \sum_{i=1}^nr_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,,\label{eqn:localisation_leakage}
\end{equation}
which in practice may correspond to their averages. We can therefore say, in the context of our proposed localisation method, LCAO leakage corresponds to the averages of sensor private information, while individual sensor information remains private. This is in line with intuition given an aggregation leakage function.
